---
title: "specindex"
author: "TZHH"
date: "07/05/2021"
output: html_document
editor_options: 
  chunk_output_type: inline
---

#TCC GUILHERME

```{r}
library(prospectr)
library(corrgram)
library(ggplot2)
library(lattice)
library(dplyr)
library(magrittr)
library(lattice)
library(latticeExtra)
library(glue)
library(ggplot2)
library(reshape2)
library(caret)
library(grid)
library(gridExtra)


pkg <- c("rgdal", "raster", "dplyr", "caret", "doParallel", "janitor", "gtools", 
         "hydroGOF", "Cubist", "randomForest", "e1071", "ggplot2", "PMCMR", 
         "rcompanion", "multcompView", "tmap", "tmaptools", "tidyr", "geobr",
         "sf", "fasterize", "beepr", "gbm", "earth", "kernlab", "stringr")
sapply(pkg, require, character.only = T)

```


```{r}
data <- read.csv("../data/SSL.csv", sep = ",")

id <- data[,1]
soc <- data[,c(19:21)] #17 DC, 18 WCT, 19 WCC
clay <- data[,c(23:25)]
soil <- cbind(soc[1], clay[1])

RAW <- data[,c(26:length(data))]
```

#Spectra index

Predictor variables using data on `spectra` according to the literature (https://docs.google.com/spreadsheets/d/1K9bVN9NI4IQNVyPyyonqCbmGQQYSgz6lyvNR2We-bno/edit?usp=sharing)


The spectral processing is indicated by the letter
* X = raw
* S = Smoothing
* G = Savitzky Golay

```{r pre proc}
SMO <- prospectr::movav(RAW, w = 9) # w = tamanho da janela (número de bandas)

SGD <- prospectr::savitzkyGolay(RAW, p = 1, w = 11, m = 1)  # p = ordem do polinomio; w = tamanho da janela; m = ordem da derivada
```

```{r Prepare index}
dat <- read.csv("../data/SLL_index.csv", sep = ";", header = F, stringsAsFactors=F)
dat <- dat[-c(1), ]
names(dat) <- dat[c(1),]
dat <- dat[-c(1), ]
dat <- as.data.frame(lapply(dat, as.numeric))

    # Remover covariaveis com na
    dat <- dat[, colSums(is.na(dat)) == 0] %>% 
      na.omit() %>% 
      na.exclude() %>% 
      drop_na()
    
    # Remover covari?veis com vari?ncia pr?xima a 0
    INDEX <- dat%>% dplyr::select(-one_of(nearZeroVar(dat, names = T)))  
```

## Model formulation

model1 - COS ~ RAW (355:2500 nm)
model2 - COS ~ SGD (355:2500 nm)
model3 - COS ~ index

model4 - argila ~ RAW (355:2500 nm)
model5 - argila ~ SGD (355:2500 nm)
model6 - argila ~ index

# data preparation
```{r}
data1 <- cbind(soil, SMO)
data2 <- cbind(soil, SGD)
data3 <- INDEX
  
data4 <- cbind(soil, SMO)
data5 <- cbind(soil, SGD)
data6 <- INDEX
```

```{r}
model1 <-  as.formula(paste("soc ~", paste(names(SMO), collapse = "+")))
model2 <-  as.formula(paste("soc ~", paste(names(SGD), collapse = "+")))
model3 <-  as.formula(paste("soc ~", paste(names(INDEX)[c(seq(4,length(INDEX)))], collapse = "+")))

model4 <-  as.formula(paste("clay ~", paste(names(SMO), collapse = "+")))
model5 <-  as.formula(paste("clay ~", paste(names(SGD), collapse = "+")))
model6 <-  as.formula(paste("clay ~", paste(names(INDEX)[c(seq(4,length(INDEX)))], collapse = "+")))
```


```{r}
vam = createDataPartition(dat$soc, p = 0.70, list = FALSE)
```


#PLS
```{r}
library(Metrics)
library(beepr)
library(caret)
           
memory.limit (9999999999)

tictoc::tic()
#vam = createDataPartition(dat$soc, p = 0.70, list = FALSE)
train <- dat[vam, ]
val <- dat[-vam, ]

#CONTROL
control <- trainControl(method = "cv", number = 10)
grid <- expand.grid(.ncomp = seq(1, 20, 1))


fit_pls <- train(fm, data = train,
                 method = 'pls',
                 trControl = control,
                 tuneGrid = grid,
                 importance = F,
                 na.action = na.omit)

fit_pls <- train(fm, data = train,
                 method = 'pls',
                 .comp = fit_pls$bestTune$ncomp,
                 importance = F,
                 na.action = na.omit)



tresult <- predict(fit_pls, train)
tresult <- data.frame(train$soc, Predicted=tresult)

rmse(train$soc, tresult$Predicted)
cor(train$soc, tresult$Predicted)^2
bias(train$soc, tresult$Predicted)
mae(train$soc, tresult$Predicted) #Mean Absolute Error
mdae(train$soc, tresult$Predicted) #Median Absolute Error

tmp <- cbind(train$id, train$soc, tresult$Predicted)
train_pred <- rbind(train_pred, tmp)

#val

vresult <- predict(fit_pls, val)
vresult <- data.frame(val$soc, Predicted=vresult)

rmse(val$soc, vresult$Predicted)
cor(val$soc, vresult$Predicted)^2
bias(val$soc, vresult$Predicted)
mae(val$soc, vresult$Predicted) #Mean Absolute Error
mdae(val$soc, vresult$Predicted) #Median Absolute Error

tictoc::toc()


write.csv(importance, "results/pls_INDEX_importance.csv")
write.csv(train_pred, "results/pls_INDEX_train_pred.csv")


beep()
```

# Figures

## Correlation index

### cor

```{r corfunction}
cor_fun <- function(x, y, method){
  tmp <- cor.test(x, y, method= method)
  cbind(r=tmp$estimate, p=tmp$p.value) }
```


```{r, warning= FALSE}
#write.csv(dataindex, "results/dataindex.csv")
dat <- read.csv("results/dataindex.csv")
dat <- dataindex
 
coscor <- t(apply(dat, 2, cor_fun, dat[, 1], "spearman"))
#write.csv(coscor, "results/CosCorr.csv")

claycor <- t(apply(dat, 2, cor_fun, dat[, 2], "spearman"))
#write.csv(claycor, "results/ClayCorr.csv")


dat <- read.csv("../data/SLL_index.csv", sep = ";", header = F, stringsAsFactors=F)
dat <- dat[-c(1), ]
names(dat) <- dat[c(1),]
dat <- dat[-c(1), ]
dat <- as.data.frame(lapply(dat, as.numeric))

 
coscor <- t(apply(dat, 2, cor_fun, dat[, 2], "spearman"))
#write.csv(coscor, "../results/CosCorr_index.csv")

claycor <- t(apply(dat, 2, cor_fun, dat[, 3], "spearman"))
#write.csv(claycor, "../results/ClayCorr_index.csv")
```


### Figure 1

Empirical probability density of carbon (A) and clay (B) content in soil samples and the theoretical normal probability density function (dashed line).
Key characteristics of the soil samples and its site, such as land use/land cover (C), and parental material (D).

```{r, eval = FALSE}

p1 <- histogram(
  ~ soc, data, 
  xlab = expression('COS, [%]'), col = 'lightgray', type = "percent", 
  panel = function (...) {
    panel.grid(v = -1, h = -1)
    panel.histogram(...)
    lattice::panel.rug(...)
  },
  page = function (n) {
    grid::grid.text(label = "A)", x = grid::unit(0.04, "npc"), y = grid::unit(0.95, "npc"))
  })# + l

p2 <- histogram(
  ~ clay, data, 
  xlab = expression('Argila,  [%]'), col = 'lightgray', type = "percent", 
  panel = function (...) {
    panel.grid(v = -1, h = -1)
    panel.histogram(...)
    lattice::panel.rug(...)
  },
  page = function (n) {
    grid::grid.text(label = "B)", x = grid::unit(0.04, "npc"), y = grid::unit(0.95, "npc"))
  })# + l


p3 <- barchart(
  data$geology, xlab = 'Material de origem', ylab = 'Percent of total', horizontal = FALSE, 
  col = 'lightgray',
  panel = function (...) {
    lattice::panel.grid(h = -1, v = 0)
    lattice::panel.barchart(...)
  },
  page = function (n) {
    grid::grid.text(label = "E)", x = grid::unit(0.04, "npc"), y = grid::unit(0.95, "npc"))
  })

p4 <- barchart(
  data$land.use, xlab = 'Uso/cobertura da terra', ylab = 'Percent of total', horizontal = FALSE, 
  col = 'lightgray',
  panel = function (...) {
    lattice::panel.grid(h = -1, v = 0)
    lattice::panel.barchart(...)
  },
  page = function (n) {
    grid::grid.text(label = "F)", x = grid::unit(0.04, "npc"), y = grid::unit(0.95, "npc"))
  })

png("results/hist-soil-samples.png")
gridExtra::grid.arrange(p1, p2, p3, p4,  ncol = 2)
dev.off()
```

### Figure 2

Correlation between soil organic carbon content and clay content in soil samples and spectra Vis-NIR-SWIR (mean = solid line, sd = grey).
```{r}
#MUDAR PRE PROCESSAMENTO

#####################################################
#########################cálculo ds curvas médias e sd 

####################
geral.spectra <- RAW

mean.geral <- apply(geral.spectra, 2 , FUN = mean) ##### mean 
sd.geral   <- apply(geral.spectra, 2 , FUN = sd) ##### sd
pos.sd.geral        <- -sd.geral ##### pos. and neg. std dev

pos        <- (mean.geral + pos.sd.geral)
neg        <- (mean.geral - pos.sd.geral)


CR.pos.sd.table       <- rbind(mean.geral, pos, neg )

CR.class.mean.pos.neg           <- (data.frame(t(CR.pos.sd.table)))
colnames(CR.class.mean.pos.neg) <- c("Mean","Pos", "Neg")
row.names(CR.class.mean.pos.neg)<- NULL

CR.class.mean.pos.neg$band      <- seq(355,2500)

geralRAW <- CR.class.mean.pos.neg

####################
geral.spectra <- SMO

mean.geral <- apply(geral.spectra, 2 , FUN = mean) ##### mean 
sd.geral   <- apply(geral.spectra, 2 , FUN = sd) ##### sd
pos.sd.geral        <- -sd.geral ##### pos. and neg. std dev

pos        <- (mean.geral + pos.sd.geral)
neg        <- (mean.geral - pos.sd.geral)


CR.pos.sd.table       <- rbind(mean.geral, pos, neg )

CR.class.mean.pos.neg           <- (data.frame(t(CR.pos.sd.table)))
colnames(CR.class.mean.pos.neg) <- c("Mean","Pos", "Neg")
row.names(CR.class.mean.pos.neg)<- NULL

CR.class.mean.pos.neg$band      <- seq(359,2496) #SMO

geralSMO <- CR.class.mean.pos.neg

#############
geral.spectra <- SGD

mean.geral <- apply(geral.spectra, 2 , FUN = mean) ##### mean 
sd.geral   <- apply(geral.spectra, 2 , FUN = sd) ##### sd
pos.sd.geral        <- -sd.geral ##### pos. and neg. std dev

pos        <- (mean.geral + pos.sd.geral)
neg        <- (mean.geral - pos.sd.geral)


CR.pos.sd.table       <- rbind(mean.geral, pos, neg )

CR.class.mean.pos.neg           <- (data.frame(t(CR.pos.sd.table)))
colnames(CR.class.mean.pos.neg) <- c("Mean","Pos", "Neg")
row.names(CR.class.mean.pos.neg)<- NULL

CR.class.mean.pos.neg$band      <- seq(359,2494) #SMO

geralSGD <- CR.class.mean.pos.neg


#####################################################
#########################SPECTRA CURVE
library(ggplot2)
library(grid)
library(gridExtra)

s1 <- ggplot2::ggplot(data = geralRAW) +
  geom_ribbon(aes(ymin = Neg, ymax = Pos, x = band), alpha = 0.4, fill="gray") +
  geom_line(aes(x = band, y = Mean), color="red", size = 1, lty =1) +
  #scale_y_continuous("Reflectance", limits = c(0, 0.35)) +
  #scale_x_continuous("Wavelength (nm)", limits = c(355,2500)) +
  theme_bw() +
   facet_grid(rows = vars("RAW")) +
    theme(strip.text.y = element_text(size=12, color="black",
                                      face="bold"))

s2 <- ggplot2::ggplot(data = geralSMO) +
  geom_ribbon(aes(ymin = Neg, ymax = Pos, x = band), alpha = 0.4, fill="gray") +
  geom_line(aes(x = band, y = Mean), color="red", size = 1, lty =1) +
  #scale_y_continuous("Reflectance", limits = c(0, 0.35)) +
  #scale_x_continuous("Wavelength (nm)", limits = c(355,2500)) +
  theme_bw() +
   facet_grid(rows = vars("SMO")) +
    theme(strip.text.y = element_text(size=12, color="black",
                                      face="bold"))

s3 <- ggplot2::ggplot(data = geralSGD) +
  geom_ribbon(aes(ymin = Neg, ymax = Pos, x = band), alpha = 0.4, fill="gray") +
  geom_line(aes(x = band, y = Mean), color="red", size = 1, lty =1) +
  #scale_y_continuous("Reflectance", limits = c(-0.001, 0.0015)) +
  #scale_x_continuous("Wavelength (nm)", limits = c(355,2500)) +
  theme_bw() +
   facet_grid(rows = vars("SGD")) +
    theme(strip.text.y = element_text(size=12, color="black",
                                      face="bold"))


#####################################################
#########################CORRELATION
###
matrix <- cbind(soil, RAW)
cormat <- round(cor(matrix),2)
melted_cormat <- reshape2::melt(cormat)
melted_cormat_RAW <-  melted_cormat %>% filter(Var1 == "soc")
melted_cormat_RAW <-  melted_cormat_RAW[-c(1:3),]
colnames(melted_cormat_RAW)[3] <- "Corr"


matrix <- cbind(soil, SMO)
cormat <- round(cor(matrix),2)
melted_cormat <- reshape2::melt(cormat)
melted_cormat_SMO <-  melted_cormat %>% filter(Var1 == "soc")
melted_cormat_SMO <-  melted_cormat_SMO[-c(1:3),]
colnames(melted_cormat_SMO)[3] <- "Corr"

####
matrix <- cbind(soil, SGD)
cormat <- round(cor(matrix),2)
melted_cormat <- reshape2::melt(cormat)
melted_cormat_SGD <-  melted_cormat %>% filter(Var1 == "soc")
melted_cormat_SGD = melted_cormat_SGD[-c(1:3),]
colnames(melted_cormat_SGD)[3] <- "Corr"

################################ argila

matrix <- cbind(soil, RAW)
cormat <- round(cor(matrix),2)
melted_cormat <- reshape2::melt(cormat)
melted_cormat_RAWc <-  melted_cormat %>% filter(Var1 == "clay")
melted_cormat_RAWc <-  melted_cormat_RAWc[-c(1:3),]
colnames(melted_cormat_RAWc)[3] <- "Corr"


matrix <- cbind(soil, SMO)
cormat <- round(cor(matrix),2)
melted_cormat <- reshape2::melt(cormat)
melted_cormat_SMOc <-  melted_cormat %>% filter(Var1 == "clay")
melted_cormat_SMOc <-  melted_cormat_SMOc[-c(1:3),]
colnames(melted_cormat_SMOc)[3] <- "Corr"

####
matrix <- cbind(soil, SGD)
cormat <- round(cor(matrix),2)
melted_cormat <- reshape2::melt(cormat)
melted_cormat_SGDc <-  melted_cormat %>% filter(Var1 == "clay")
melted_cormat_SGDc = melted_cormat_SGDc[-c(1:3),]
colnames(melted_cormat_SGDc)[3] <- "Corr"

#range(melted_cormat_SMO$value)
#range(melted_cormat_SGD$value)
#range(melted_cormat_CRR$value)

#specCorr <- rbind(melted_cormat_SMO, melted_cormat_SGD, melted_cormat_CRR)
#write.csv(specCorr, "../result/specCorr.csv")

#####################################################
#########################PLOT

## pegar legenda
#p0 <-  ggplot(data = melted_cormat_RAW, aes(x=Var1, y=Var2, fill=Corr)) + 
#  geom_tile() +
#  scale_fill_gradient2(low="navy", mid="white", high="red", 
 #                      midpoint=0, limits=range(c(-1:1))) +
#  coord_flip()
#legend <- cowplot::get_legend(p0)
#####

p1 <-  ggplot(data = melted_cormat_RAW, aes(x=Var1, y=Var2, fill=Corr)) + 
  geom_tile() +
  xlab(" ") + ylab(" ") +
  #theme(legend.position = "none") +
  scale_fill_gradient2(low="navy", mid="white", high="red", 
                       midpoint=0, limits=range(c(-1:1))) +
  coord_flip()

p2 <-  ggplot(data = melted_cormat_SMO, aes(x=Var1, y=Var2, fill= Corr)) + 
  geom_tile() +
  xlab(" ") + ylab(" ") +
  #theme(legend.position = "none") +
  scale_fill_gradient2(low="navy", mid="white", high="red", 
                       midpoint=0, limits=range(c(-1:1))) +
  coord_flip()

p3 <-  ggplot(data = melted_cormat_SGD, aes(x=Var1, y=Var2, fill=Corr)) + 
  geom_tile() +
  xlab(" ") + ylab(" ") +
  #theme(legend.position = "none") +
  scale_fill_gradient2(low="navy", mid="white", high="red", 
                       midpoint=0, limits=range(c(-1:1))) +
  coord_flip()

p4 <-  ggplot(data = melted_cormat_RAWc, aes(x=Var1, y=Var2, fill=Corr)) + 
  geom_tile() +
  xlab(" ") + ylab(" ") +
  #theme(legend.position = "none") +
  scale_fill_gradient2(low="navy", mid="white", high="red", 
                       midpoint=0, limits=range(c(-1:1))) +
  coord_flip()

p5 <-  ggplot(data = melted_cormat_SMOc, aes(x=Var1, y=Var2, fill= Corr)) + 
  geom_tile() +
  xlab(" ") + ylab(" ") +
  #theme(legend.position = "none") +
  scale_fill_gradient2(low="navy", mid="white", high="red", 
                       midpoint=0, limits=range(c(-1:1))) +
  coord_flip()

p6 <-  ggplot(data = melted_cormat_SGDc, aes(x=Var1, y=Var2, fill=Corr)) + 
  geom_tile() +
  xlab(" ") + ylab(" ") +
  #theme(legend.position = "none") +
  scale_fill_gradient2(low="navy", mid="white", high="red", 
                       midpoint=0, limits=range(c(-1:1))) +
  coord_flip()


#ggpubr::ggarrange(s1, p1, s2, p2, s3, p3, ncol=1, nrow=6, common.legend = TRUE, legend="bottom")


png("results/Spectra_corr_SMO.png")
ggpubr::ggarrange(s2, p2, p5,  ncol=1, nrow=3)
dev.off()

png("results/Spectra_corr_SGD.png")
ggpubr::ggarrange(s3, p3, p6,  ncol=1, nrow=3)
dev.off()

png("results/Spectra_corr.svg")
ggpubr::ggarrange(s2, p1, p4, s2, p2, p5, s3, p3, p6,  ncol=1, nrow=9)
dev.off()

```
